Water discharge quantity has a variable impact on sediment transport capacity in subglacial channels

### 2023-09-22 Delaneyetal2023b.tex
Draft to pass around

\authors{Ian Delaney\affil{1},  Daniel Farinotti\affil{2,3},  Andrew J. Tedstone\affil{4},   Mauro A. Werder\affil{2,3}}

\affiliation{1}{Institut des dynamiques de la surface terrestre (IDYST), Universit\'{e} de Lausanne, B\^{a}timent G\'{e}opolis, 1015 Lausanne, Switzerland}
\affiliation{2}{Laboratory of Hydraulics, Hydrology and Glaciology (VAW), ETH-Z\"urich, H\"onggerbergring 26, 8093 89 Z\"urich, Switzerland}
\affiliation{3}{Swiss Federal Institute for Forest, Snow and Landscape Research (WSL) Z\"uricherstrasse 111, 8903 1011 Birmensdorf, Switzerland}
\affiliation{4}{Department of Geosciences, University of Fribourg, Ch. du Musée 1700, Fribourg, Switzerland}

>>>>

\authors{Ian Delaney\affil{1},  Andrew J. Tedstone\affil{2},   Mauro A. Werder\affil{3,4},  Daniel Farinotti\affil{3,4}, }

\affiliation{1}{Institut des dynamiques de la surface terrestre (IDYST), Universit\'{e} de Lausanne, B\^{a}timent G\'{e}opolis, 1015 Lausanne, Switzerland}
\affiliation{2}{Department of Geosciences, University of Fribourg, Ch. du Musée 1700, Fribourg, Switzerland}
\affiliation{3}{Laboratory of Hydraulics, Hydrology and Glaciology (VAW), ETH-Z\"urich, H\"onggerbergring 26, 8093 89 Z\"urich, Switzerland}
\affiliation{4}{Swiss Federal Institute for Forest, Snow and Landscape Research (WSL) Z\"uricherstrasse 111, 8903 1011 Birmensdorf, Switzerland}
